---
title: "Question 3"
---

The Mann Whitney statistic is one of the non parametric statistic to describe how different two samples are.
SUppose $X_i, i=1,...,n$ and $Y_j, j=1,...,m$ are two observations from two populations. The Mann-Whitney statistic
is computed as

$$
U = \sum_{i=1}^n \sum_{j=1}^m S(X_i, Y_j)
$$
where

$$
S(x,y) = \begin{cases}
1, & \text{ if } x > y \\
1/2, & \text{ if } x = y\\
0, & \text{ if } x < y. \\
\end{cases}
$$
This is a naive R implemention.
```{r}
mwstatR <- function(x, y) {
    sum(outer(x, y, `>`)) + 0.5 * sum(outer(x, y, `==`))
}
```

```{r}
n <- 1e3
x <- runif(n)
y <- runif(n)
s <- mwstatR(x, y)
```

##### (a) Write an R function which uses `for` loops instead of `outer` to caclulate the MW statistic.


```{r}
mwstatR2 <- function(x, y) {
    
}
```

```{r}
all.equal(s, mwstatR2(x, y))
```


##### (b) write a function `mwstatC` in Rcpp which calculates the MW statistic between two numeric vectors `x` and `y`. (Assume that `x` and `y` do not contain missing values).



```{r}
all.equal(s, mwstatC(x, y))
```


##### (b) Benchmark the functions with inputs of different lengths (`n = 10, 100, 1000`), comment on the results.


